```{r}
library(GGally)
library(lmtest)
library(tidymodels)
library(tidyverse)
```

```{r}
air = airquality

str(air)
summary(air)
```
```{r}
nrow(air)
ncol(air)
```
```{r}
colnames(air)[colSums(is.na(air)) > 0]
```

```{r}
air2 <- drop_na(air)

summary(air2)
```

```{r}
ncol(air2)
nrow(air2)
```

```{r}
ggpairs(air2)
```

```{r}
ggcorr(air2, label = TRUE)
```

#Plot temp as a predictor for ozone starting with ggplot

```{r}
ggplot(air2, aes(x=Temp, y=Ozone))+
  geom_point()

ggplot(air2, aes(x=Temp, y=Ozone))+
  geom_point() +
  theme_bw() #white out the background of the plot for easier viewing
```
#Plot linear regression on a model with temp to predict ozone
```{r}
air_recipe = recipe(Ozone ~ Temp, air2) #lr recipe

lm_model = #give the model type a name
linear_reg() %>% #specify linear regression
set_engine("lm") #specify the specify type of linear tool 

lm_wflow = workflow() %>%
add_model(lm_model) %>%
add_recipe(air_recipe)

lm_fit = fit(lm_wflow, air2)

summary(lm_fit$fit$fit$fit)

```
#Y intercept of linear regression model is -147.6 with a slope of 2.4391
#notice p-value of temp as a predictor for ozone IS significant with p-value <.05 ***

```{r}
confint(lm_fit$fit$fit$fit)


```
#If temp = 80 degrees, what is the predicted ozone level?
```{r}
predict(lm_fit,data.frame("Temp"=80))
```
#If temp = 32 degrees, what is the predicted ozone level?
```{r}
 predict(lm_fit,data.frame("Temp"=32))
```

#There are 4 linear regression model assumptions. Are any of the assumptions violated?

#1: Evidence of autocorrelation is not noted in the ggplot.
#2: Evidence of non-independent residuals? I must do a Durbin Watson Test
```{r}
dwtest(lm_fit$fit$fit$fit)
```
#p-value greater than 0.05 fails to reject null (no evidence of non-independent residuals)

#3 Evidence of obvious/severe difference in residual variance. I must plot residuals.
```{r}
air2 = air2 %>% mutate(resid1 = lm_fit$fit$fit$fit$residuals)
ggplot(air2,aes(x=Temp,y=resid1)) + geom_point()
```
#3 Residuals plot is concentrated around -25 to 25 with no obvious differences that are concerning.

#4 Residuals appear to have normality. I must plot residuals again.
```{r}
ggplot(air2,aes(x=resid1)) + geom_histogram()
```
#Kinda concerning, what about the isolated bin at the top? Needs further checking because the bulk of the data (highest counts) are centered around zero. Perhaps I need to change the bins.


